Title: A proof-of-concept study

### 2022-01-12 paper.tex
update

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center.]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__gammaRay.png}
  \caption{The simulated photon flux at  2 GeV (top), 10 GeV (middle), and 100 GeV (bottom).}
  \label{fig__gammaRay}
\end{figure*}

>>>>

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
               Copyright 2015 American Physical Society.)\
               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center, and the view point .]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ \citep{Selig2015} and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}
